Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-02 paper/paper.qmd
model changes

## Model
Let Y denote the memory game score, then

$$
\text{Y}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
$$

Where:

- $\beta_0$ is the intercept.

- $\beta_1$, $\beta_2$, and $\beta_3$ are coefficients for the predictors and interaction term.

- $\varepsilon_i$ is the random error term.

```{r, echo = FALSE}
#| label: tbl-model-result
#| tbl-cap: "Regression Results for Memory Game Score"
#| echo: false
#| warning: false
#| message: false

@@

@@

```{r, echo = FALSE}
#| label: tbl-model-fit
#| tbl-cap: "Model Fit Statistics for Memory Game Score"
#| echo: false
#| warning: false
#| message: false

Where:

- $Y_{ijk}$: Memory score
- $\mu$: Overall mean  
- $\alpha_i$: Effect of the $i^{\text{th}}$ drug  
- $\beta_j$: Effect of the $j^{\text{th}}$ dosage level  
- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
- $\varepsilon_{ijk} \sim \mathcal{N}(0, \sigma^2)$: Random error

>>>>

## Model

We model the memory game score using a two-way ANOVA with interaction between drug type and dosage level. The general statistical form of the model is

Where

- $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level  
- $\mu$: Overall mean  
- $\alpha_i$: Effect of the $i$-th drug (categorical with 4 levels)  
- $\beta_j$: Effect of the $j$-th dosage level (categorical with 2 levels)  
- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
- $\epsilon_{ijk} \sim N(0, \sigma^2)$ : Random error

After dummy coding the categorical variables, the model used in our analysis can be expressed as:

 \begin{align*}
Y_i =\ & \beta_0 
+ \beta_1 \cdot \text{Paracetamol}_i 
+ \beta_2 \cdot \text{Placebo}_i 
+ \beta_3 \cdot \text{Tramadol}_i \\
& + \beta_4 \cdot \text{LowDosage}_i 
+ \beta_5 \cdot (\text{Paracetamol}_i \times \text{LowDosage}_i) \\
& + \beta_6 \cdot (\text{Placebo}_i \times \text{LowDosage}_i) 
+ \beta_7 \cdot (\text{Tramadol}_i \times \text{LowDosage}_i)
+ \varepsilon_i
\end{align*}

Where

- $\beta_0$: Intercept (Aspirin at High dosage — the reference group)  
- $\beta_1, \beta_2, \beta_3$: Main effects of Paracetamol, Placebo, and Tramadol relative to Aspirin  
- $\beta_4$: Effect of Low dosage relative to High  
- $\beta_5, \beta_6, \beta_7$: Interaction effects for each drug under Low dosage  
- $\epsilon_i$: Residual error for the $i$-th participant

```{r, echo = FALSE}
#| label: tbl-model-result
#| tbl-cap: "Coefficient Estimates from Linear Model for Memory Game Score"
#| echo: false
#| warning: false
#| message: false

@@

anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)

model_tidy <- tidy(anova_model) %>%
  rename(
    `Predictor Term` = term,
    `Estimate` = estimate,
    `Std. Error` = std.error,
    `t-statistic` = statistic,
    `p-value` = p.value
  )

kable(model_tidy, format = "latex", booktabs = TRUE)
```

```{r, echo = FALSE}
#| label: tbl-model-fit
#| tbl-cap: "Model Summary Statistics for Memory Game Score"
#| echo: false
#| warning: false
#| message: false

model_glance <- glance(anova_model) %>%
  transmute(
    `F-Statistic` = statistic,
    `Model df` = df,
    `Residual df` = df.residual,
    `p-value` = p.value,
    `Residual Std. Error` = sigma,
    `Sample Size (n)` = nobs
  )

kable(model_glance, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down")

@@
